### 2023-01-03 Manuscript/Draft1.Rmd
updating manuscript

- Climate change is happening
 Due to a combination of climate change and shifts in circulation, the Northeast United States continental shelf has experienced rapid warming in recent decades, resulting in a shift in spatial distributions of many species. Since stock assessment models rely on accurate descriptions of population dynamics and contemporary patterns of spatial abundance, there is concern that rapid undocumented changes in spatial distributions of species will bias future stock assessments. The implication of this is that the bottom trawl survey is actually sampling the population during a different life cycle stage than was originally assumed, which can lead to biased stock assessments. We are therefore interested in analyzing the impact of climate change on the accuracy of future stock assessment models as measured by NOAA’s ongoing bottom-trawl survey along the East coast.

@@

>>>>

- Climate change is happening

 Due to a combination of climate change and shifts in circulation, the Northeast United States continental shelf has experienced rapid warming in recent decades, resulting in a shift in spatial distributions of many species. Since stock assessment models rely on accurate descriptions of population dynamics and contemporary patterns of spatial abundance, there is concern that rapid undocumented changes in spatial distributions of species will bias future stock assessments. The implication of this is that the bottom trawl survey is actually sampling the population during a different life cycle stage than was originally assumed, which can lead to biased stock assessments. We are therefore interested in analyzing the impact of climate change on the accuracy of future stock assessment models as measured by NOAA’s ongoing bottom-trawl survey along the East coast.

@@

```{r CodERROR,echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
library("knitr")
library("kableExtra")
library("dplyr")
library("readr")
library("tidyr")
library("forcats")

param_table1 = read_csv("Cod_results.csv")

summary_tab1 <- param_table1 %>% 
# Group the table according to Parameter, Scenario
  group_by(Temp)%>%
  mutate(Temp = factor(Temp)) %>%
  arrange(Temp) %>%
  select(Temp, everything())

# Create table to present the data]
Fig_3a <-  kable(summary_tab1[, -1], 
  caption = "Cod error results.",
    format = "latex", booktabs = TRUE) %>%
  kable_styling(font_size = 10) %>%
  pack_rows(tab_kable(), colnum = 1,
    index = table(fct_inorder(summary_tab1$Temp), useNA = "no"))
```

```{r, results='asis'}
Fig_3a
```

### 2023-01-03 Manuscript/Draft1.tex
attemps at citations
updating manuscript

\begin{itemize}
\item
  Climate change is happening
  Due to a combination of climate change and shifts in circulation, the Northeast United States continental shelf has experienced rapid warming in recent decades, resulting in a shift in spatial distributions of many species. Since stock assessment models rely on accurate descriptions of population dynamics and contemporary patterns of spatial abundance, there is concern that rapid undocumented changes in spatial distributions of species will bias future stock assessments. The implication of this is that the bottom trawl survey is actually sampling the population during a different life cycle stage than was originally assumed, which can lead to biased stock assessments. We are therefore interested in analyzing the impact of climate change on the accuracy of future stock assessment models as measured by NOAA's ongoing bottom-trawl survey along the East coast.
\item
  say something about our study species? Past abundance history, biological characteristics, others? Maybe better suited in below section
\end{itemize}

@@

\caption{\label{tab:unnamed-chunk-1}Cod error results}
\centering
\begin{tabular}[t]{l|l|l|l|r|r|r|l|l}
\hline
Temp & Strata & Noise & season & VAST.No.Cov & VAST.w..Cov & Stratified.Mean & X & X.1\\
\hline
const & all & no & spring & 0.11 & 0.12 & 0.36 & NA & \\
\hline
const & all & yes & spring & 0.12 & 0.15 & 0.35 & NA & Cod\\
\hline
const & all & no & fall & 0.19 & 0.05 & 0.49 & NA & Decreasing Population\\
\hline
const & all & yes & fall & 0.30 & 0.23 & 0.41 & NA & \\
\hline
const & reduced & no & spring & 0.17 & 0.24 & 0.41 & NA & \\
\hline
const & reduced & yes & spring & 0.20 & 0.23 & 0.46 & NA & \\
\hline
const & reduced & no & fall & 0.21 & 0.33 & 0.60 & NA & \\
\hline
const & reduced & yes & fall & 0.18 & 0.31 & 0.58 & NA & \\
\hline
increasing & all & no & spring & 0.12 & 0.15 & 0.25 & NA & \\
\hline
increasing & all & yes & spring & 0.19 & 0.19 & 0.27 & NA & \\
\hline
increasing & all & no & fall & 0.76 & 0.13 & 0.45 & NA & \\
\hline
increasing & all & yes & fall & 0.89 & 0.33 & 0.44 & NA & \\
\hline
increasing & reduced & no & spring & 0.14 & 0.22 & 0.32 & NA & \\
\hline
increasing & reduced & yes & spring & 0.15 & 0.21 & 0.29 & NA & \\
\hline
increasing & reduced & no & fall & 0.60 & 0.31 & 0.54 & NA & \\
\hline
increasing & reduced & yes & fall & 0.62 & 0.32 & 0.53 & NA & \\
\hline
\end{tabular}
\end{table}

@@

@@

\multicolumn{3}{l}{\textbf{all}}\\

@@

\multicolumn{3}{l}{\textbf{reduced}}\\

@@

>>>>

\begin{itemize}
\tightlist
\item
  Climate change is happening
\end{itemize}

Due to a combination of climate change and shifts in circulation, the Northeast United States continental shelf has experienced rapid warming in recent decades, resulting in a shift in spatial distributions of many species. Since stock assessment models rely on accurate descriptions of population dynamics and contemporary patterns of spatial abundance, there is concern that rapid undocumented changes in spatial distributions of species will bias future stock assessments. The implication of this is that the bottom trawl survey is actually sampling the population during a different life cycle stage than was originally assumed, which can lead to biased stock assessments. We are therefore interested in analyzing the impact of climate change on the accuracy of future stock assessment models as measured by NOAA's ongoing bottom-trawl survey along the East coast.

\begin{itemize}
\tightlist
\item
  say something about our study species? Past abundance history, biological characteristics, others? Maybe better suited in below section
\end{itemize}

@@

\caption{\label{tab:unnamed-chunk-1}Cod error results}
\centering
\begin{tabular}[t]{l|l|l|l|r|r|r}
\hline
Temp & Strata & Noise & season & VAST.No.Cov & VAST.w..Cov & Stratified.Mean\\
\hline
constant & all & no & spring & 0.11 & 0.12 & 0.36\\
\hline
constant & all & yes & spring & 0.12 & 0.15 & 0.35\\
\hline
constant & all & no & fall & 0.19 & 0.05 & 0.49\\
\hline
constant & all & yes & fall & 0.30 & 0.23 & 0.41\\
\hline
constant & reduced & no & spring & 0.17 & 0.24 & 0.41\\
\hline
constant & reduced & yes & spring & 0.20 & 0.23 & 0.46\\
\hline
constant & reduced & no & fall & 0.21 & 0.33 & 0.60\\
\hline
constant & reduced & yes & fall & 0.18 & 0.31 & 0.58\\
\hline
increasing & all & no & spring & 0.12 & 0.15 & 0.25\\
\hline
increasing & all & yes & spring & 0.19 & 0.19 & 0.27\\
\hline
increasing & all & no & fall & 0.76 & 0.13 & 0.45\\
\hline
increasing & all & yes & fall & 0.89 & 0.33 & 0.44\\
\hline
increasing & reduced & no & spring & 0.14 & 0.22 & 0.32\\
\hline
increasing & reduced & yes & spring & 0.15 & 0.21 & 0.29\\
\hline
increasing & reduced & no & fall & 0.60 & 0.31 & 0.54\\
\hline
increasing & reduced & yes & fall & 0.62 & 0.32 & 0.53\\
\hline
\end{tabular}
\end{table}

@@

\multicolumn{1}{l}{\textbf{all}}\\

@@

@@

\multicolumn{1}{l}{\textbf{reduced}}\\

@@

\caption{\label{tab:CodERROR}Cod error results.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lllrrr}
\toprule
Strata & Noise & season & VAST No Cov & VAST w/ Cov & Stratified Mean\\
\midrule
\addlinespace[0.3em]
\multicolumn{1}{l}{\textbf{constant}}\\
\hspace{1em}all & no & spring & 0.11 & 0.12 & 0.36\\
\hspace{1em}all & yes & spring & 0.12 & 0.15 & 0.35\\
\hspace{1em}all & no & fall & 0.19 & 0.05 & 0.49\\
\hspace{1em}all & yes & fall & 0.30 & 0.23 & 0.41\\
\hspace{1em}reduced & no & spring & 0.17 & 0.24 & 0.41\\
\hspace{1em}reduced & yes & spring & 0.20 & 0.23 & 0.46\\
\hspace{1em}reduced & no & fall & 0.21 & 0.33 & 0.60\\
\hspace{1em}reduced & yes & fall & 0.18 & 0.31 & 0.58\\
\addlinespace[0.3em]
\multicolumn{1}{l}{\textbf{increasing}}\\
\hspace{1em}all & no & spring & 0.12 & 0.15 & 0.25\\
\hspace{1em}all & yes & spring & 0.19 & 0.19 & 0.27\\
\hspace{1em}all & no & fall & 0.76 & 0.13 & 0.45\\
\hspace{1em}all & yes & fall & 0.89 & 0.33 & 0.44\\
\hspace{1em}reduced & no & spring & 0.14 & 0.22 & 0.32\\
\hspace{1em}reduced & yes & spring & 0.15 & 0.21 & 0.29\\
\hspace{1em}reduced & no & fall & 0.60 & 0.31 & 0.54\\
\hspace{1em}reduced & yes & fall & 0.62 & 0.32 & 0.53\\
\bottomrule
\end{tabular}
\end{table}
